False Sign Rate Illustration

### 2015-06-23 examples/fsr.rmd
update

@@

```{r}
opts_chunk$set(fig.path='figure/lfsr/')
set.seed(100)
library(ashr)
library(qvalue)
n = 10000
beta = rnorm(n)
sebetahat = 1
betahat = beta + rnorm(n,0,sebetahat)

@@

In this example, at a $p$ value threshold of 0.05, $\ash$ estimates the local false sign rate (lfsr) to be `r max(z.ash$lfsr[p<0.05])` and the tail false sign rate (FSR) to be `r mean(z.ash$lfsr[p<0.05])`. The actual FSR at that threshold is `r mean(sign(z[p<0.05])!=sign(beta[p<0.05]))`.

>>>>

---
title: "False Sign Rate Illustration"
output: html_document
---

@@

```{r}
#opts_chunk$set(fig.path='figure/lfsr/')
set.seed(100)
library(ashr)
library(qvalue)
n = 10000
beta = rnorm(n)
sebetahat = 1
betahat = beta + rnorm(n,0,sebetahat)

@@

In this example, at a $p$ value threshold of 0.05, $\ash$ estimates the local false sign rate (lfsr) to be `r max(z.ash$lfsr[p<0.05])` and the tail false sign rate (FSR) to be `r mean(z.ash$lfsr[p<0.05])`. The actual FSR at that threshold is `r mean(sign(z[p<0.05])!=sign(beta[p<0.05]))`.
(The conservative estimates from $\ash$ are likely partly due to our deliberate use of a penalty term to provide conservative estimates of $\pi_0$.)
